\documentclass[12pt]{article}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{tikz}

\counterwithin*{equation}{section}
\counterwithin*{equation}{subsection}
\addtolength\parskip{\bigskipamount}

\graphicspath{ {./images/} } 

\begin{document}
\section{Limits}
\underline{Definition:}\[
	\lim_{(x,y) \to (a,b)} f(x,y) = L
\]
\textbf{if} we can make the values of \(f(x,y)\) as close to \(L\) as we like by taking the point \((x,y)\) sufficiently close to the point \((a,b)\), but not equal to \((a,b)\). 

Appendix D reading

\begin{itemize}
	\item There can often be many ways to approach a limit.
	\item Therefore, easier to show that a limit does not exist.
\end{itemize}
If \(f(x,y)\rightarrow L_1\) , as \((x,y)\rightarrow (a,b)\)  along curve \(C_1\) \\
and \(f(x,y)\rightarrow L_2\) , as \((x,y)\rightarrow (a,b)\) along curve \(C_2\), \\
where \(L_1 != L_2\) , then \[
	\lim_{(x,y) \to (a,b)} f(x,y) = DNE
\] 

\subsubsection{Limits Example 1}
Show that the limit does not exist.\\
a) \[\lim_{(x,y) \to (0,0)} \frac{x^2-y^2}{x^2+y^2}\] 
b) \[
	\lim_{(x,y) \to (0,0)} \frac{xy}{x^2+y^2} 
\]
c) \[
	\lim_{(x,y) \to (0,0)} \frac{xy^2}{x^2+y^4}
\]

\subsection{Limit Laws}
Shared with previously known limit laws.
\begin{itemize}
	\item \(\lim(f\pm y) = \lim(f) \pm \lim(y) \)
	\item \(\lim(fy) = (\lim(f))(\lim(y))\) 
	\item \(\lim(\frac{f}{g}) = \frac{\lim(f)}{\lim(g)}\) , if \(\lim(g) \ne 0 \) 
\end{itemize}

\subsubsection{Squeeze Theorem}
\underline{Example}: Evaluate \[
	\lim_{(x,y) \to (0,0)} \frac{5xy^2}{x^2+y^2}
\]
\section{Continuity}
\underline{Definition}: \(f\) is continuous at \((a,b)\) if \[
	\lim_{(x,y) \to (a,b)} f(x,y) = f(a,b)
\]
\(f\) is continuous on \(D\) if \(f\) is continuous at every point \((a,b) \in D\) 
\begin{itemize}
	\item All polynomials are continuous on \(\mathbb{R}^2\) 
	\item All rational functions are continuous on their domains.
\end{itemize}
\subsubsection{Continuity Example 1}
Compute: \[
	\lim_{(x,y) \to (2,1)} (xy^2+x^2y^3-5x+3y)
\]
\subsubsection{Continuity Example 2}
Where is \(f(x,y) = \frac{x^2-y^2}{x^2+y^2}\) continuous?
\subsubsection{Continuity Example 3}
	Present in notes

\subsection{Composition of Continuous Functions}
if \(f:\mathbb{R}^2 \rightarrow \mathbb{R}\) and \(g:\mathbb{R}\rightarrow \mathbb{R}\) are both continuous, then \(h=g\cdot f \) is also continuous 
\subsubsection{Comp. of Cont. Functions Example 1}
Where is \(h(x,y)=\arctan(\frac{x}{y}) \) continuous?

\subsubsection{Exercise: Comp. of Cont. Functions}
Find the limit if it exists:\\
a) \[
	\lim_{(x,y) \to (6,3)} xy\cos(x-2y)
\]
Take the limit
\begin{align}
	(6)(3)\cos((6)-2(3))\\
	(18)\cos(0) = 19
\end{align}
b) \[
	\lim_{(x,y) \to (0,0)} \frac{x^2+\sin^2y}{2x^2 + y^2}
\]
c) \[
	\lim_{(x,y) \to (0,0)} \frac{6x^3y}{2x^4+y^4}
\]
d) \[
	\lim_{(x,y) \to (0,0)} \frac{x^2+\sin^2y}{x^2+2y^2}
\]
e) \[
	\lim_{(x,y) \to (0,0)} \frac{xy^4}{x^2+y^8}
\]
f) \[
	\lim_{(x,y) \to (0,0)} \frac{x^4+y^4}{x^2+y^2}
\] \end{document}

